Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-03-22 PAPER.tex
made notes of where to flesh out jackknife section

\begin{itemize}
%\item Original Data (black): This is identical to the unweighted, revised PAPER-64 power spectrum in Figure \ref{fig:ps1_data} (one baseline type only) with weighting matrix $\textbf{I}$. There are clear detections at low $k$'s.
\item Baselines: We split our dataset into two halves, where each contains half of the total baselines used in the 
analysis. No baselines are repeated between the two datasets.
\item Sidereal Hour: We split our dataset into two halves based on LST, namely the first half (LSTs 0.5-4.6 hours) and second half (LSTs 
4.6-8.6 hours).
\item Day: We split our dataset into even and odd Julian days. We form power spectra for each separately, only cross-multiplying `even' with `even', for example. Although we don't allow this in our standard pipeline, we include these same-dataset cross-multiplications to allow a power spectrum to be estimated from solely the `even' data (similarly for `odd'). If the same sky signal is in both the `even' and `odd' datasets, we expect it to cancel out. However, allowing these cross-multiplications can in practice introduce a low level noise bias... 
\end{itemize}

\begin{figure*}
	\centering
	\includegraphics[width=0.47\textwidth]{plots/null_bls.png}
	\includegraphics[width=0.47\textwidth]{plots/null_lsts.png}
	\includegraphics[width=0.47\textwidth]{plots/null_eo.png}
	\caption{Power spectrum results (with $2\sigma$ errors) for three null tests, where a jackknife is taken along the baseline axis (top left), LST axis (top right), and even/odd Julian date axis (bottom). The results shown are unweighted (no signal loss), where the power spectrum values plotted are computed from the difference between two power spectra of a jackknife. The gray shaded region in each plot is the estimated $2\sigma$ theoretical noise limit given the parameters of each test. We find that there are no significant systematics that differ between the tests, though there are low level biases at high-$k$ values in both the LST test (likely due to foregrounds that vary in LST) and even/odd test (likely due to thermal noise squaring). All three tests are dominated by residual foregrounds at $k$-values near the horizon ($k\sim\pm 0.1$ $h$Mpc$^{-1}$), which is not surprising given that foregrounds are brightest in this region post-delay filtering.}
	\label{fig:null}
\end{figure*}

@@

The even/odd test shows $81\%$ of all error bars being consistent with zero, with several power spectrum points falling outside the estimated error region. Rather than attribute these biases to systematics that differ \textit{between} the `even' and `odd' datasets, we believe that they are caused by the squaring of thermal noise (which was allowed in the construction of this test). This supports our choice to not allow the cross-multiplication between the same LST-binned datasets in our full pipeline.

>>>>

\begin{itemize}
%\item Original Data (black): This is identical to the unweighted, revised PAPER-64 power spectrum in Figure \ref{fig:ps1_data} (one baseline type only) with weighting matrix $\textbf{I}$. There are clear detections at low $k$'s.
\item Baselines: We split our dataset into two halves, where each contains half of the total baselines used in the 
analysis. No baselines are repeated between the two datasets.
\item Sidereal Hour: We split our dataset into two halves based on LST, namely the first half (LSTs 0.5-4.6 hours) and second half (LSTs 
4.6-8.6 hours).
\item Day: We split our dataset into even and odd Julian days. We form power spectra for each separately, only cross-multiplying `even' with `even', for example. Although we don't allow this in our standard pipeline, we include these same-dataset cross-multiplications to allow a power spectrum to be estimated from solely the `even' data (similarly for `odd'). If the same sky signal is in both the `even' and `odd' datasets, we expect it to cancel out. %However, allowing these cross-multiplications can in practice introduce a low level noise bias... 
\end{itemize}

\begin{figure*}
	\centering
	\includegraphics[width=0.47\textwidth]{plots/null_bls.png}
	\includegraphics[width=0.47\textwidth]{plots/null_lsts.png}
	\includegraphics[width=0.47\textwidth]{plots/null_eo.png}
	\caption{Power spectrum results (with $2\sigma$ errors) for three null tests, where a jackknife is taken along the baseline axis (top left), LST axis (top right), and even/odd Julian date axis (bottom). The results shown are unweighted (no signal loss), where the power spectrum values plotted are computed from the difference between two power spectra of a jackknife. The gray shaded region in each plot is the estimated $2\sigma$ theoretical noise limit given the parameters of each test. We find that there are no significant systematics that differ between the tests, though there are low level biases at high-$k$ values in both the LST test (likely due to foregrounds that vary in LST) and even/odd test (likely due to \cc{??}). All three tests are dominated by residual foregrounds at $k$-values near the horizon ($k\sim\pm 0.1$ $h$Mpc$^{-1}$), which is not surprising given that foregrounds are brightest in this region post-delay filtering.}
	\label{fig:null}
\end{figure*}

@@

The even/odd test shows $81\%$ of all error bars being consistent with zero, with several power spectrum points falling outside the estimated error region. \cc{why is that?} %Rather than attribute these biases to systematics that differ \textit{between} the `even' and `odd' datasets, we believe that they are caused by the squaring of thermal noise (which was allowed in the construction of this test). This supports our choice to not allow the cross-multiplication between the same LST-binned datasets in our full pipeline.
